The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-04-14 paper.tex
update subsection{Landmark Line Regions and Measurements}

\subsection{Landmark Line Regions and Measurements}
Measurements consist of references to sections, the start point, midpoint, end point, and short definitions.

>>>>

\subsection{Landmark Line Regions and Measurements}
Landmark line regions are lines connecting or outlining landmarks (e.g., an edge between two landmarks, an angle between three landmarks 
or an outline of one or more landmarks).
The landmark line regions can be measured (e.g., the length of the edge or outline and the angle degree).
Such measurements can be used to derive/determine individual phenotypes.

Measurements consist of references to sections, the start point, midpoint, end point, and short definitions.
